---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PFIweeds2020

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of PFIweeds2020 is to grant easy access to data and analysis functions for the 2020 Practical Farmers of Iowa project looking at the effect of cover-cropping on the weed seedbank.

Someday I will put a map of the sampling locations here!

## Installation

The development version from [GitHub](https://github.com/) can be accessed with:

``` r
# install.packages("devtools")
devtools::install_github("vanichols/PFIweeds2020")
```

## Example

An example won't really do much good here. 

```{r example}
library(PFIweeds2020)
## basic example code
```

